---
title: "Cleaning and Analysis"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages

```{r}
library(ggpubr)
library(ggsignif)
library(tidyverse)
library(viridis)
```

## Data 

```{r}
sales_data <- read.csv("/Users/kenjinchang/github/multimodal-framework-validation/data/daily-sales-counts.csv") 
foot_traffic_data <- read.csv("/Users/kenjinchang/github/multimodal-framework-validation/data/daily-sales-traffic.csv")
emissions_data <- read.csv("/Users/kenjinchang/github/multimodal-framework-validation/data/parent-data/item-kg-co2e.csv")
water_data <- read.csv("/Users/kenjinchang/github/multimodal-framework-validation/data/parent-data/item-l-h2o-blue.csv")
historical_data <- read.csv("/Users/kenjinchang/github/multimodal-framework-validation/data/parent-data/historical-transaction-volume.csv")
ingredient_level_footprint_data <- read.csv("/Users/kenjinchang/github/multimodal-framework-validation/data/parent-data/ingredient-level-footprint-calculations.csv")
```

## Cleaning (Global)

### Inconsistencies between sales categories and stations

The first item we'll have to address involves the discrepancies in how items are categorized within the point-of-sale (POS) system and the physical dining environment. 

In particular, the "Asian," "Grill," and "Italian" sales categories, as they are represented within `sales_data` by the POS system, are—in reality—each representing two independent station concepts: the "Ramen" and "Wok" concepts for the "Asian" category, the "Grill" and "Quesadilla" concepts for the "Grill" category, and the "Pasta" and "Pizza" concepts for the "Italian" category. We will also make corresponding changes to the "Mexican" sales category, which flags sales from the "Wrap" station concept.

To help us incorporate this information, we'll first use the following code chunks to tease out both the names and number of unique items listed under each of the nine sales categories.

```{r}
sales_data %>%
  group_by(sales_cat) %>%
  distinct(item) %>%
  arrange(sales_cat,item) %>%
  head(5)
```

```{r}
sales_data %>%
  group_by(sales_cat) %>%
  distinct(item) %>%
  count()
```

With these, we are able to easily reference the information needed to perform two initial checks: one to see whether there are identical items—be them modifications, mains, or sides—with the same name sold under different sales categories and another to see if there are identical items with different names sold under the same sales category.

```{r}
sales_data %>%
  group_by(sales_cat) %>%
  distinct(item) %>%
  arrange(item,sales_cat) 
```

From these initial checks, we can tease out a few things: 

* The modification used to indicate whether a guest added a beef patty to their order is represented differently under the "Grill" sales category depending on whether the sale was made during Fall 2024 (i.e., "ADD Beef Patty $2.99") or Spring 2025 (i.e., "ADD Beef Patty").

* "Side Potato Tots" is listed with the same name under both the "Grill" sales category and the "Grab N Go" sales category. During Fall 2024, "Side Potato Tots" sales were categorized under the "Grab N Go" sales category whereas, during Spring 2025, they were categorized under "Grill." 

Furthermore, from our understanding of how the listed items are physically arranged within the dining context, we can also use these checks to determine whether there are items that are represented consistently both within and across sales categories but filed under a category other than the one that where they are sold.

* "Fried Chicken Tenders" are categorized under the "Grill" sales category despite being sold alongside the items listed under "Grab N Go." Because part of our analysis relies on understanding how diners choose between main, side, and modification options at the "Grill," specifically, we will instead opt to file sales of "Fried Chicken Tenders" under "Grab N Go."

Given this, we'll make the following changes for consistency: 

* We will adjust the item name for the beef-patty modification so that it is consistent across the two study periods (i.e., "+ Beef Patty").


```{r}
sales_data$item <- gsub("\\$", "",sales_data$item)
sales_data <- sales_data %>%
  mutate(item=str_replace_all(item,"ADD Beef Patty 2.99","+ Beef Patty")) %>%
  mutate(item=str_replace_all(item,"ADD Beef Patty","+ Beef Patty"))
```

* We will categorize "Side Potato Tots" and "Fried Chicken Tenders" under the "Grab N Go" sales category across both study periods.

```{r}
sales_data <- sales_data %>% 
  mutate(sales_cat=case_when(item=="Side Potato Tots"~"Grab N Go",
                             TRUE ~ sales_cat)) %>%
  mutate(sales_cat=case_when(item=="Fried Chicken Tenders"~"Grab N Go",
                             TRUE ~ sales_cat))
```

With these initial checks performed, and the prescribed changes addressed, we can now move on to resolve the inconsistencies between the sales categories created via the POS system and the station concepts where those items are actually sold. We will accomplish this by creating a new categorical variable, `station`, that pairs items according to the stations where they are sold within the physical dining environment. 

```{r}
sales_data %>%
  group_by(sales_cat) %>%
  distinct(item) %>%
  arrange(sales_cat,item) 
```

```{r}
sales_data <- sales_data %>% 
  mutate(station=case_when(item=="1 Entree + 1 Side"~"Wok",
                           item=="1 Entree + 2 Side"~"Wok",
                           item=="1 Wok Entree"~"Wok",
                           item=="2 Entrees + 2 Sides"~"Wok",
                           item=="Add Extra Toppings"~"Ramen",
                           item=="Bowl Ramen Chicken"~"Ramen",
                           item=="Bowl Ramen Pork"~"Ramen",
                           item=="Bowl Ramen Tofu"~"Ramen",
                           item=="Side Fried Spring Roll"~"Wok",
                           item=="Side Vegetable Spring Rolls"~"Wok",
                           item=="Side Vegetables"~"Wok",
                           item=="Side Vegetarian Fried Rice with"~"Wok",
                           item=="Side Vegetarian Lo Mein"~"Wok",
                           item=="Side White or Brown Rice"~"Wok",
                           item=="2 Slices Toast"~"Breakfast",
                           item=="Add Bacon"~"Breakfast",
                           item=="Burrito Breakfast"~"Breakfast",
                           item=="Egg Cheese Bacon Breakfast Sandw"~"Breakfast",
                           item=="Egg Cheese Sausage Breakfast San"~"Breakfast",
                           item=="Grand Slam Breakfast"~"Breakfast",
                           item=="PC Butter"~"Breakfast",
                           item=="PC Jelly"~"Breakfast",
                           item=="PC Peanut Butter"~"Breakfast",
                           item=="Pancake Single"~"Breakfast",
                           item=="Small French Omelet"~"Breakfast",
                           item=="Toast"~"Breakfast",
                           item=="Trillium Home Fries"~"Breakfast",
                           item=="Two Eggs"~"Breakfast",
                           item=="LTO Sandwich"~"Deli",
                           item=="Burrito Breakfast G&G"~"Grab N Go",
                           item=="Egg Cheese Bacon Breakfast Sandwich"~"Grab N Go",
                           item=="Egg Cheese Sausage Breakfast Sandwich"~"Grab N Go",
                           item=="LTO Meatball Sub"~"Grab N Go",
                           item=="LTO Spicy Chicken Sandwich"~"Grab N Go",
                           item=="Side Potato Tots"~"Grab N Go",
                           item=="+ Beef Patty"~"Grill",
                           item=="ADD Burger Salmon Grilled"~"Grill",
                           item=="ADD Cheese"~"Grill",
                           item=="ADD Chicken Breast"~"Grill",
                           item=="Add Egg .99"~"Grill",
                           item=="Add Impossible Burger Patty"~"Grill",
                           item=="Add Sausage 2 Patty"~"Grill",
                           item=="Black Bean Burger"~"Grill",
                           item=="Burrito Una Mano Trillium BYO"~"Quesadilla",
                           item=="French Fries"~"Grill",
                           item=="Fried Chicken Tenders"~"Grab N Go",
                           item=="Grilled Chicken Breast Sandwich"~"Grill",
                           item=="Grilled Hamburger"~"Grill",
                           item=="Quesadilla Cheese"~"Quesadilla",
                           item=="Quesadilla Deluxe Trillium"~"Quesadilla",
                           item=="Seared Salmon Burger"~"Grill",
                           item=="Sweet Potato Fries"~"Grill",
                           item=="Trillium Grill Impossible Burger"~"Grill",
                           item=="Add Extra Meat"~"Pasta",
                           item=="Create Your Pasta Bowl MEAT"~"Pasta",
                           item=="Create Your Pasta Bowl VEG"~"Pasta",
                           item=="Pizza Cheese"~"Pizza",
                           item=="Pizza with Toppings"~"Pizza",
                           item=="Side Bread Pasta Station"~"Pasta",
                           item=="Add Extra Toppings Una Mano"~"Wrap",
                           item=="Burrito Bowl BYO"~"Wrap",
                           item=="Side Guacamole"~"Wrap",
                           item=="Side Salsa"~"Wrap",
                           item=="Side Sour Cream"~"Wrap",
                           item=="Single Taco"~"Wrap",
                           item=="Add Extra Protein 2.99"~"Salad Bar",
                           item=="Add Extra Protein 3.99"~"Salad Bar",
                           item=="Salad by the Pound"~"Salad Bar",
                           item=="8 oz Soup"~"Soup",
                           item=="Soup 12 oz"~"Soup"))
```

Then, we perform a few quick checks to ensure all of the items were coded as intended, without duplicates or typos.

```{r}
sum(is.na(sales_data$station))
```

```{r}
sales_data %>%
  distinct(station)
```

### Correcting known input errors

For the next stage of our cleaning process, we corresponded with our research partners at the dining facility to clarify how we ought to treat the sales of items that were noticeably absent from the previously reviewed dining menus. In particular, we noted that, at the "Ramen" station, there were recorded sales of "Bowl Ramen Pork," despite this not being an advertised offering within the dining facility during either of the two study periods.

Our site partners noted that these were likely input errors that occurred at the register, in part because it was a previously programmed option to accommodate sales of this item during a prior time period. They correspondingly advised that we should map those purchases onto sales of "Bowl Ramen Chicken," as opposed to "Bowl Ramen Tofu," on the basis that it was more likely that a sales assistant would visually misidentify chicken as pork—as opposed to tofu-at check-out.

As such, we make the following change:

```{r}
sales_data <- sales_data %>% 
  mutate(item=str_replace_all(item,"Bowl Ramen Pork","Bowl Ramen Chicken")) 
```

### Distinguishing between mains, modifications, and sides

In the interest of separating our analysis between the different types of items listed within `sales_data`, we will create a new categorical variable, `item_cat` specifying each sales tally according to whether the item references the sale of a side, a main, or a modification made to a main. 

```{r}
sales_data <- sales_data %>%
  mutate(item_cat=case_when(item=="1 Entree + 1 Side"~"Main",
                           item=="1 Entree + 2 Side"~"Main",
                           item=="1 Wok Entree"~"Main",
                           item=="2 Entrees + 2 Sides"~"Main",
                           item=="Add Extra Toppings"~"Modification",
                           item=="Bowl Ramen Chicken"~"Main",
                           item=="Bowl Ramen Pork"~"Main",
                           item=="Bowl Ramen Tofu"~"Main",
                           item=="Side Fried Spring Roll"~"Side",
                           item=="Side Vegetable Spring Rolls"~"Side",
                           item=="Side Vegetables"~"Side",
                           item=="Side Vegetarian Fried Rice with"~"Side",
                           item=="Side Vegetarian Lo Mein"~"Side",
                           item=="Side White or Brown Rice"~"Side",
                           item=="2 Slices Toast"~"Side",
                           item=="Add Bacon"~"Modification",
                           item=="Burrito Breakfast"~"Main",
                           item=="Egg Cheese Bacon Breakfast Sandw"~"Main",
                           item=="Egg Cheese Sausage Breakfast San"~"Main",
                           item=="Grand Slam Breakfast"~"Main",
                           item=="PC Butter"~"Side",
                           item=="PC Jelly"~"Side",
                           item=="PC Peanut Butter"~"Side",
                           item=="Pancake Single"~"Side",
                           item=="Small French Omelet"~"Side",
                           item=="Toast"~"Side",
                           item=="Trillium Home Fries"~"Side",
                           item=="Two Eggs"~"Side",
                           item=="LTO Sandwich"~"Main",
                           item=="Burrito Breakfast G&G"~"Main",
                           item=="Egg Cheese Bacon Breakfast Sandwich"~"Main",
                           item=="Egg Cheese Sausage Breakfast Sandwich"~"Main",
                           item=="LTO Meatball Sub"~"Main",
                           item=="LTO Spicy Chicken Sandwich"~"Main",
                           item=="Side Potato Tots"~"Side",
                           item=="+ Beef Patty"~"Modification",
                           item=="ADD Burger Salmon Grilled"~"Modification",
                           item=="ADD Cheese"~"Modification",
                           item=="ADD Chicken Breast"~"Modification",
                           item=="Add Egg .99"~"Modification",
                           item=="Add Impossible Burger Patty"~"Modification",
                           item=="Add Sausage 2 Patty"~"Modification",
                           item=="Black Bean Burger"~"Main",
                           item=="Burrito Una Mano Trillium BYO"~"Main",
                           item=="French Fries"~"Side",
                           item=="Fried Chicken Tenders"~"Side",
                           item=="Grilled Chicken Breast Sandwich"~"Main",
                           item=="Grilled Hamburger"~"Main",
                           item=="Quesadilla Cheese"~"Main",
                           item=="Quesadilla Deluxe Trillium"~"Main",
                           item=="Seared Salmon Burger"~"Main",
                           item=="Sweet Potato Fries"~"Side",
                           item=="Trillium Grill Impossible Burger"~"Main",
                           item=="Add Extra Meat"~"Modification",
                           item=="Create Your Pasta Bowl MEAT"~"Main",
                           item=="Create Your Pasta Bowl VEG"~"Main",
                           item=="Pizza Cheese"~"Main",
                           item=="Pizza with Toppings"~"Main",
                           item=="Side Bread Pasta Station"~"Side",
                           item=="Add Extra Toppings Una Mano"~"Modification",
                           item=="Burrito Bowl BYO"~"Main",
                           item=="Side Guacamole"~"Side",
                           item=="Side Salsa"~"Side",
                           item=="Side Sour Cream"~"Side",
                           item=="Single Taco"~"Main",
                           item=="Add Extra Protein 2.99"~"Modification",
                           item=="Add Extra Protein 3.99"~"Modification",
                           item=="Salad by the Pound"~"Main",
                           item=="8 oz Soup"~"Main",
                           item=="Soup 12 oz"~"Main"))
```

As we did before, we will perform a series of checks to ensure the new variable was coded as intended.

```{r}
sum(is.na(sales_data$item_cat))
```

```{r}
sales_data %>%
  distinct(item_cat)
```

### Distinguishing between meal periods and treatment and non-treatment stations

We use the following code chunks to, first, list out each of the relevant stations and, subsequently, designate them (using `station_type`) as either satellite (i.e., used to measure effects on sales outside of the treated stations) or treatment-receiving (i.e.,used to measure within-station changes in food choice). More specifically, this will offer us an initial, within-period indicator of reactance (i.e., whether there are decreases in sales that temporally correlate with the implementation of any of the various treatment-menu conditions).

```{r}
sales_data %>%
  distinct(station) %>%
  arrange(station)
```

```{r}
sales_data <- sales_data %>%
  mutate(station_type=case_when(station=="Breakfast"~"Satellite",
                                station=="Deli"~"Satellite",
                                station=="Grab N Go"~"Satellite",
                                station=="Grill"~"Treatment",
                                station=="Pasta"~"Satellite",
                                station=="Pizza"~"Satellite",
                                station=="Quesadilla"~"Satellite",
                                station=="Ramen"~"Treatment",
                                station=="Salad Bar"~"Satellite",
                                station=="Soup"~"Satellite",
                                station=="Wok"~"Satellite",
                                station=="Wrap"~"Satellite")) 
```

We will additionally create a new variable, `meal_period`, to distinguish between the different service windows represented within `sales_data`. More specifically, to offer a contrary between-indicator of reactance, we will use the coded categories (i.e., "Breakfast" and "Lunch") to monitor for whether the phases during which the different menu conditions were implemented were associated with any decreases in sales volumes.

```{r}
sales_data <- sales_data %>%
  mutate(meal_period=case_when(station=="Breakfast"~"Breakfast",
                                station=="Deli"~"Lunch",
                                station=="Grab N Go"~"Lunch",
                                station=="Grill"~"Lunch",
                                station=="Pasta"~"Lunch",
                                station=="Pizza"~"Lunch",
                                station=="Quesadilla"~"Lunch",
                                station=="Ramen"~"Lunch",
                                station=="Salad Bar"~"Lunch",
                                station=="Soup"~"Lunch",
                                station=="Wok"~"Lunch",
                                station=="Wrap"~"Lunch")) 
```

### Mapping dish-level emissions, water, and cost estimates onto items

In our companion repo, we had—during the planning phases of this project—collated life-cycle analysis data to estimate the carbon and blue-water costs associated with each of the dishes on offer at the two treated stations. In part, the purpose of this recipe modeling was to enable precise estimations for the carbon- and water-footprint labels used during some of the treatment phases of the study. Another virtue of this work, however, is that it also enables us to understand how diner food choices map on to their corresponding climate and resource costs. In other words, we are able to use these figures to help calculate the mean emissions and water costs associated with item sales at each station across the various menu conditions trialed. This enables us to reasonably detect whether the sustainability of diners' food choices improved during the treatment phases, outside of the simpler proportions used to investigate whether the highest- and lowest-emitting options were chosen less and more, respectively. 

To avoid premature rounding, we will recalculate the emissions and resource costs associated with the various mains, modifications, and sides on offer at both the "Grill" and "Ramen" stations, rather than use the estimates used to populate the descriptive footprint labels.

We'll start with process by pairing each of the qualifying offerings with their corresponding water and emissions costs. As a reminder, these are the sales item we need to find correspond carbon- and water-cost data for:

```{r}
sales_data %>%
  filter(station=="Grill" | station=="Ramen") %>%
  distinct(item) %>%
  arrange()
```

We'll begin by pairing the calculated water- and carbon-footprint estimates to each corresponding composite item (i.e., an item comprised of more than one ingredient, as defined by the research partner's recipe system): 

```{r}
composite_item_pairing <- ingredient_level_footprint_data %>%
  group_by(recipe) %>%
  summarise(ind_carbon_cost=sum(kg_co2e),ind_water_cost=sum(l_h2o_blue)) %>%
  filter(recipe=="[CYO Grill Component] Burger" | recipe=="[CYO Grill Component] Fries" | recipe=="[CYO Grill Component] Chicken Sandwich" | recipe=="[CYO Grill Component] Salmon Burger" | recipe=="[CYO Grill Component] Impossible Burger" | recipe=="[CYO Grill Component] Sweet Potato Fries" | recipe=="[CYO Grill Component] Black Bean Burger" | recipe=="[CYO Ramen Component] Chicken Bowl" | recipe=="[CYO Ramen Component] Tofu Bowl" | recipe=="[CYO Ramen Component] Ginger Tare") %>%
  mutate(item=case_when(recipe=="[CYO Grill Component] Black Bean Burger"~"Black Bean Burger",
                        recipe=="[CYO Grill Component] Burger"~"Grilled Hamburger",
                        recipe=="[CYO Grill Component] Chicken Sandwich"~"Grilled Chicken Breast Sandwich",
                        recipe=="[CYO Grill Component] Fries"~"French Fries",
                        recipe=="[CYO Grill Component] Impossible Burger"~"Trillium Grill Impossible Burger",
                        recipe=="[CYO Grill Component] Salmon Burger"~"Seared Salmon Burger",
                        recipe=="[CYO Grill Component] Sweet Potato Fries"~"Sweet Potato Fries",
                        recipe=="[CYO Ramen Component] Chicken Bowl"~"Bowl Ramen Chicken",
                        recipe=="[CYO Ramen Component] Ginger Tare"~"Add Extra Toppings",
                        recipe=="[CYO Ramen Component] Tofu Bowl"~"Bowl Ramen Tofu")) %>%
  select(item,ind_carbon_cost,ind_water_cost)
```

This leaves us with seven items left to pair, each of which are listed within the recipe system as single ingredients (i.e., simple recipes). We'll handle the "ADD Cheese" modification separately because, unlike the remaining six items, this option requires us to calculate the average cost associated with each of the six different topping varieties offered. 

```{r}
variable_item_pairing <- ingredient_level_footprint_data %>%
  filter(station=="Grill") %>%
  filter(recipe=="[CYO Grill Component] Toppings, American Cheese" | recipe=="[CYO Grill Component] Toppings, Cheddar Cheese" | recipe=="[CYO Grill Component] Toppings, Pepper Jack Cheese" | recipe=="[CYO Grill Component] Toppings, Provolone Cheese" | recipe=="[CYO Grill Component] Toppings, Blue Cheese" | recipe=="[CYO Grill Component] Toppings, Vegan Cheese") %>%
  select(recipe,kg_co2e,l_h2o_blue) %>% 
  mutate(item="ADD Cheese") %>%
  group_by(item) %>%
  summarise(ind_carbon_cost=mean(kg_co2e),ind_water_cost=mean(l_h2o_blue))
```

With that sorted, we can now move on to the last six remaining simple recipes:

```{r}
simple_item_pairing <- ingredient_level_footprint_data %>%
  filter(ingredient=="80/20 Beef Patty" | ingredient=="\"Impossible Burger\" Patty [Patty \"Impossible Burger\" Trillium]" | ingredient=="Bacon Pork Raw" | ingredient=="5 Oz Bnls Skinles Chicken Breast" | ingredient=="Salmon Burger Patty" | ingredient=="Egg Whole Fresh Medium Flat [Egg Sous Vide]") %>%
  select(ingredient,kg_co2e,l_h2o_blue) %>%
  mutate(item=case_when(ingredient=="80/20 Beef Patty"~"+ Beef Patty",
                        ingredient=="5 Oz Bnls Skinles Chicken Breast"~"ADD Chicken Breast",
                        ingredient=="Salmon Burger Patty"~"ADD Burger Salmon Grilled",
                        ingredient=="\"Impossible Burger\" Patty [Patty \"Impossible Burger\" Trillium]"~"Add Impossible Burger Patty",
                        ingredient=="Bacon Pork Raw"~"Add Sausage 2 Patty",
                        ingredient=="Egg Whole Fresh Medium Flat [Egg Sous Vide]"~"Add Egg .99")) %>%
  rename(ind_carbon_cost=kg_co2e,ind_water_cost=l_h2o_blue) %>%
  select(item,ind_carbon_cost,ind_water_cost) %>%
  distinct()
```

Now that we've mapped the corresponding emissions- and resource-costs associated with each of the items offered at the treatment station, we can perform a join to incorporate this information into `sales_data`. Before that, though, we need to add the monetary costs of each changes, too, to help us understand whether sales revenue varied across the different menu conditions trialled.

While we have most of the pricing information available to accomplish this, we assume a flat 2.99 fee for all additional patty modifications, with the exception of the "Add Sausage 2 Patty" modification, which instead maps on to the bacon addition presented on the "Grill" menu. We also assume a $0.99 fee "Add Extra Toppings" modification at the "Ramen" station, which maps on to the Ginger Tare that appears in our recipe modeling.

```{r}
item_pairing <- bind_rows(composite_item_pairing,variable_item_pairing,simple_item_pairing)
item_pairing <- item_pairing %>%
  mutate(ind_dollar_cost=case_when(item=="Black Bean Burger"~8.69,
                                  item=="Grilled Hamburger"~8.99,
                                  item=="Grilled Chicken Breast Sandwich"~8.49,
                                  item=="French Fries"~2.99,
                                  item=="Trillium Grill Impossible Burger"~10.49,
                                  item=="Seared Salmon Burger"~8.49,
                                  item=="Sweet Potato Fries"~2.99,
                                  item=="Bowl Ramen Chicken"~9.49,
                                  item=="Add Extra Toppings"~.99,
                                  item=="Bowl Ramen Tofu"~9.49,
                                  item=="ADD Cheese"~1.99,
                                  item=="+ Beef Patty"~2.99,
                                  item=="ADD Chicken Breast"~2.99,
                                  item=="ADD Burger Salmon Grilled"~2.99,
                                  item=="Add Impossible Burger Patty"~2.99,
                                  item=="Add Sausage 2 Patty"~1.99,
                                  item=="Add Egg .99"~.99))
item_pairing
```

Now, we can add the individual, item-level costs for each of the mains, modifications, and sides sold at the two treatment stations.

```{r}
sales_data <- left_join(sales_data,item_pairing,join_by(item))
```

In addition to adding `ind_carbon_cost`, `ind_water_cost`, and `ind_dollar_cost` to `sales_data`, which map on to the individual costs of each of the items sold at the treatment stations, we will also add `corr_carbon_cost`, `corr_water_cost`, and `corr_dollar_cost`, which will map on to the corespoding costs of each of the items sold at the treatment stations. These variables will instead represent the daily aggregated costs associated with the sales of those items, based on the total quantity sold.

```{r}
sales_data <- sales_data %>%
  mutate(corr_carbon_cost=count*ind_carbon_cost) %>%
  mutate(corr_water_cost=count*ind_water_cost) %>%
  mutate(corr_dollar_cost=count*ind_dollar_cost) 
write.csv(sales_data,"/Users/kenjinchang/github/multimodal-framework-validation/data/cleaned_daily-sales-counts.csv")
```

### Separating global dataset into study-level dataasets 

With these global changes to `sales_data` now incorporated, we can separate the data according to observation period.

```{r}
fall_data <- sales_data %>%
  filter(semester=="Fall 2024")
spring_data <- sales_data %>%
  filter(semester=="Spring 2025")
```

## Cleaning and Analysis (Fall 2024)

The object of the first study is to understand how diner meal choices compared across the four menu conditions trialed. More specifically, we wish to form these comparisons by monitoring specific changes in the following outcome variables: 

* `prop_low`: The proportion of lowest-carbon mains purchased at each treated station (i.e., the quotient of the number of lowest-carbon mains sold during each menu condition divided by the total number of mains sold at that station).

* `prop_high`: The proportion of highest-carbon mains purchased at each treated station (i.e., the quotient of the number of highest-carbon mains sold during each menu condition divided by the total number of mains sold at that station).

* `mean_carbon_cost`: The mean emissions cost across the mains, sides, and modifications sold at each treated station (i.e., the quotient of the aggregated emissions costs for the items sold at each treated station divided by the total number of items sold).

* `mean_spend`: The average revenue gained on mains, sides, and modifications at each treated station (i.e., the quotient of the aggregated revenue for gained for the items sold at each treated station divided by the total number of items sold).

### Proportion of lowest-carbon selections

```{r}
fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(menu_condition,station,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop_low=case_when(item=="Black Bean Burger" & menu_condition=="Carbon Label" ~ total_count/(32+159+935+74+85),
                            item=="Bowl Ramen Tofu" & menu_condition=="Carbon Label" ~ total_count/(685+135),
                            item=="Black Bean Burger" & menu_condition=="Control" ~ total_count/(19+125+776+68+60),
                            item=="Bowl Ramen Tofu" & menu_condition=="Control" ~ total_count/(563+108),
                            item=="Black Bean Burger" & menu_condition=="Default" ~ total_count/(33+167+904+76+90),
                            item=="Bowl Ramen Tofu" & menu_condition=="Default" ~ total_count/(698+172),
                            item=="Black Bean Burger" & menu_condition=="Multimodal" ~ total_count/(41+165+1157+125+107),
                            item=="Bowl Ramen Tofu" & menu_condition=="Multimodal" ~ total_count/(860+182))) %>%
  drop_na(prop_low)
```
```{r}
fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(menu_condition,station,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop_low=case_when(item=="Black Bean Burger" & menu_condition=="Carbon Label" ~ total_count/(32+159+935+74+85),
                            item=="Bowl Ramen Tofu" & menu_condition=="Carbon Label" ~ total_count/(685+135),
                            item=="Black Bean Burger" & menu_condition=="Control" ~ total_count/(19+125+776+68+60),
                            item=="Bowl Ramen Tofu" & menu_condition=="Control" ~ total_count/(563+108),
                            item=="Black Bean Burger" & menu_condition=="Default" ~ total_count/(33+167+904+76+90),
                            item=="Bowl Ramen Tofu" & menu_condition=="Default" ~ total_count/(698+172),
                            item=="Black Bean Burger" & menu_condition=="Multimodal" ~ total_count/(41+165+1157+125+107),
                            item=="Bowl Ramen Tofu" & menu_condition=="Multimodal" ~ total_count/(860+182))) %>%
  drop_na(prop_low) %>%
  ggplot(aes(x=menu_condition,y=prop_low,fill=station)) +
  geom_col(position="dodge") + 
  scale_x_discrete(limits=c("Control","Carbon Label","Default","Multimodal"))
```

daily prop-low

```{r}
daily_prop_low_fall_data <- fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(date,menu_condition,station,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop_low=case_when(item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="1-Nov"~total_count/(94),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="1-Nov"~total_count/(47),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="10-Dec"~total_count/(72),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="10-Dec"~total_count/(41),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="11-Dec"~total_count/(68),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="11-Dec"~total_count/(49),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="11-Nov"~total_count/(112),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="11-Nov"~total_count/(81),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="12-Dec"~total_count/(99),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="12-Dec"~total_count/(55),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="12-Nov"~total_count/(134),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="12-Nov"~total_count/(95),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="13-Dec"~total_count/(66),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="13-Dec"~total_count/(57),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="13-Nov"~total_count/(139),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="13-Nov"~total_count/(91),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="14-Nov"~total_count/(145),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="14-Nov"~total_count/(99),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="15-Nov"~total_count/(94),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="15-Nov"~total_count/(76),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="16-Dec"~total_count/(70),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="16-Dec"~total_count/(47),
                             item=="Black Bean Burger"&menu_condition=="Control"&date=="16-Oct"~total_count/(123),
                             item=="Bowl Ramen Tofu"&menu_condition=="Control"&date=="16-Oct"~total_count/(104),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="17-Dec"~total_count/(87),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="17-Dec"~total_count/(41),
                             item=="Black Bean Burger"&menu_condition=="Control"&date=="17-Oct"~total_count/(153),
                             item=="Bowl Ramen Tofu"&menu_condition=="Control"&date=="17-Oct"~total_count/(82),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="18-Dec"~total_count/(71),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="18-Dec"~total_count/(46),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="18-Nov"~total_count/(130),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="18-Nov"~total_count/(77),
                             item=="Black Bean Burger"&menu_condition=="Control"&date=="18-Oct"~total_count/(89),
                             item=="Bowl Ramen Tofu"&menu_condition=="Control"&date=="18-Oct"~total_count/(65),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="19-Dec"~total_count/(50),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="19-Dec"~total_count/(14),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="19-Nov"~total_count/(167),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="19-Nov"~total_count/(98),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="2-Dec"~total_count/(118),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="2-Dec"~total_count/(113),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="20-Dec"~total_count/(39),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="20-Dec"~total_count/(23),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="20-Nov"~total_count/(129),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="20-Nov"~total_count/(99),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="21-Nov"~total_count/(144),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="21-Nov"~total_count/(97),
                             item=="Black Bean Burger"&menu_condition=="Control"&date=="21-Oct"~total_count/(143),
                             item=="Bowl Ramen Tofu"&menu_condition=="Control"&date=="21-Oct"~total_count/(85),
                             item=="Black Bean Burger"&menu_condition=="Default"&date=="22-Nov"~total_count/(76),
                             item=="Bowl Ramen Tofu"&menu_condition=="Default"&date=="22-Nov"~total_count/(57),
                             item=="Black Bean Burger"&menu_condition=="Control"&date=="22-Oct"~total_count/(163),
                             item=="Bowl Ramen Tofu"&menu_condition=="Control"&date=="22-Oct"~total_count/(83),
                             item=="Black Bean Burger"&menu_condition=="Control"&date=="23-Oct"~total_count/(135),
                             item=="Bowl Ramen Tofu"&menu_condition=="Control"&date=="23-Oct"~total_count/(92),
                             item=="Black Bean Burger"&menu_condition=="Control"&date=="24-Oct"~total_count/(145),
                             item=="Bowl Ramen Tofu"&menu_condition=="Control"&date=="24-Oct"~total_count/(107),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="25-Nov"~total_count/(98),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="25-Nov"~total_count/(66),
                             item=="Black Bean Burger"&menu_condition=="Control"&date=="25-Oct"~total_count/(97),
                             item=="Bowl Ramen Tofu"&menu_condition=="Control"&date=="25-Oct"~total_count/(53),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="26-Nov"~total_count/(75),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="26-Nov"~total_count/(51),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="28-Oct"~total_count/(127),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="28-Oct"~total_count/(76),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="29-Oct"~total_count/(145),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="29-Oct"~total_count/(80),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="3-Dec"~total_count/(131),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="3-Dec"~total_count/(97),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="30-Oct"~total_count/(132),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="30-Oct"~total_count/(82),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="31-Oct"~total_count/(149),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="31-Oct"~total_count/(89),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="4-Dec"~total_count/(146),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="4-Dec"~total_count/(97),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="4-Nov"~total_count/(114),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="4-Nov"~total_count/(85),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="5-Dec"~total_count/(173),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="5-Dec"~total_count/(92),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="5-Nov"~total_count/(138),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="5-Nov"~total_count/(84),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="6-Dec"~total_count/(103),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="6-Dec"~total_count/(76),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="6-Nov"~total_count/(137),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="6-Nov"~total_count/(107),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="7-Nov"~total_count/(142),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="7-Nov"~total_count/(97),
                             item=="Black Bean Burger"&menu_condition=="Carbon Label"&date=="8-Nov"~total_count/(107),
                             item=="Bowl Ramen Tofu"&menu_condition=="Carbon Label"&date=="8-Nov"~total_count/(73),
                             item=="Black Bean Burger"&menu_condition=="Multimodal"&date=="9-Dec"~total_count/(128),
                             item=="Bowl Ramen Tofu"&menu_condition=="Multimodal"&date=="9-Dec"~total_count/(77))) %>%
  drop_na(prop_low) %>%
  mutate(date=case_when(date=="16-Oct"~"2024-10-16",
                        date=="17-Oct"~"2024-10-17",
                        date=="18-Oct"~"2024-10-18",
                        date=="21-Oct"~"2024-10-21",
                        date=="22-Oct"~"2024-10-22",
                        date=="23-Oct"~"2024-10-23",
                        date=="24-Oct"~"2024-10-24",
                        date=="25-Oct"~"2024-10-25",
                        date=="28-Oct"~"2024-10-28",
                        date=="29-Oct"~"2024-10-29",
                        date=="30-Oct"~"2024-10-30",
                        date=="31-Oct"~"2024-10-31",
                        date=="1-Nov"~"2024-11-1",
                        date=="4-Nov"~"2024-11-4",
                        date=="5-Nov"~"2024-11-5",
                        date=="6-Nov"~"2024-11-6",
                        date=="7-Nov"~"2024-11-7",
                        date=="8-Nov"~"2024-11-8",
                        date=="11-Nov"~"2024-11-11",
                        date=="12-Nov"~"2024-11-12",
                        date=="13-Nov"~"2024-11-13",
                        date=="14-Nov"~"2024-11-14",
                        date=="15-Nov"~"2024-11-15",
                        date=="18-Nov"~"2024-11-18",
                        date=="19-Nov"~"2024-11-19",
                        date=="20-Nov"~"2024-11-20",
                        date=="21-Nov"~"2024-11-21",
                        date=="22-Nov"~"2024-11-22",
                        date=="25-Nov"~"2024-11-25",
                        date=="26-Nov"~"2024-11-26",
                        date=="2-Dec"~"2024-12-2",
                        date=="3-Dec"~"2024-12-3",
                        date=="4-Dec"~"2024-12-4",
                        date=="5-Dec"~"2024-12-5",
                        date=="6-Dec"~"2024-12-6",
                        date=="9-Dec"~"2024-12-9",
                        date=="10-Dec"~"2024-12-10",
                        date=="11-Dec"~"2024-12-11",
                        date=="12-Dec"~"2024-12-12",
                        date=="13-Dec"~"2024-12-13",
                        date=="16-Dec"~"2024-12-16",
                        date=="17-Dec"~"2024-12-17",
                        date=="18-Dec"~"2024-12-18",
                        date=="19-Dec"~"2024-12-19",
                        date=="20-Dec"~"2024-12-20")) %>%
  mutate(date=as.Date(date)) 
```

```{r}
dates_vline <- as.Date(c("2024-10-28","2024-11-11","2024-11-25"))
dates_vline <- which(daily_prop_low_fall_data$date %in% dates_vline)
```

```{r}
ggplot(daily_prop_low_fall_data,aes(x=date,y=prop_low,color=station)) + 
  geom_smooth() + 
  geom_point() +
  geom_vline(xintercept=as.numeric(daily_prop_low_fall_data$date[dates_vline]),linetype=2)
```

### Proportion of highest-emitting selections

```{r}
fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(menu_condition,station,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop_high=case_when(item=="Grilled Hamburger" & menu_condition=="Carbon Label" ~ total_count/(32+159+935+74+85),
                            item=="Bowl Ramen Chicken" & menu_condition=="Carbon Label" ~ total_count/(685+135),
                            item=="Grilled Hamburger" & menu_condition=="Control" ~ total_count/(19+125+776+68+60),
                            item=="Bowl Ramen Chicken" & menu_condition=="Control" ~ total_count/(563+108),
                            item=="Grilled Hamburger" & menu_condition=="Default" ~ total_count/(33+167+904+76+90),
                            item=="Bowl Ramen Chicken" & menu_condition=="Default" ~ total_count/(698+172),
                            item=="Grilled Hamburger" & menu_condition=="Multimodal" ~ total_count/(41+165+1157+125+107),
                            item=="Bowl Ramen Chicken" & menu_condition=="Multimodal" ~ total_count/(860+182))) %>%
  drop_na(prop_high)
```
```{r}
fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(menu_condition,station,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop_high=case_when(item=="Grilled Hamburger" & menu_condition=="Carbon Label" ~ total_count/(32+159+935+74+85),
                            item=="Bowl Ramen Chicken" & menu_condition=="Carbon Label" ~ total_count/(685+135),
                            item=="Grilled Hamburger" & menu_condition=="Control" ~ total_count/(19+125+776+68+60),
                            item=="Bowl Ramen Chicken" & menu_condition=="Control" ~ total_count/(563+108),
                            item=="Grilled Hamburger" & menu_condition=="Default" ~ total_count/(33+167+904+76+90),
                            item=="Bowl Ramen Chicken" & menu_condition=="Default" ~ total_count/(698+172),
                            item=="Grilled Hamburger" & menu_condition=="Multimodal" ~ total_count/(41+165+1157+125+107),
                            item=="Bowl Ramen Chicken" & menu_condition=="Multimodal" ~ total_count/(860+182))) %>%
  drop_na(prop_high) %>%
  ggplot(aes(x=menu_condition,y=prop_high,fill=station)) +
  geom_col(position="dodge") + 
  scale_x_discrete(limits=c("Control","Carbon Label","Default","Multimodal"))
```

Now on a daily level to see if there are diminishing effects over time across each menu condition

```{r}
fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(date,station) %>%
  summarise(daily_station_count=sum(count)) 
```

```{r}
fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(date,menu_condition,station,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop_high=case_when(item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="1-Nov"~total_count/(94),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="1-Nov"~total_count/(47),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="10-Dec"~total_count/(72),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="10-Dec"~total_count/(41),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="11-Dec"~total_count/(68),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="11-Dec"~total_count/(49),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="11-Nov"~total_count/(112),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="11-Nov"~total_count/(81),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="12-Dec"~total_count/(99),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="12-Dec"~total_count/(55),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="12-Nov"~total_count/(134),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="12-Nov"~total_count/(95),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="13-Dec"~total_count/(66),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="13-Dec"~total_count/(57),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="13-Nov"~total_count/(139),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="13-Nov"~total_count/(91),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="14-Nov"~total_count/(145),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="14-Nov"~total_count/(99),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="15-Nov"~total_count/(94),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="15-Nov"~total_count/(76),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="16-Dec"~total_count/(70),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="16-Dec"~total_count/(47),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="16-Oct"~total_count/(123),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="16-Oct"~total_count/(104),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="17-Dec"~total_count/(87),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="17-Dec"~total_count/(41),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="17-Oct"~total_count/(153),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="17-Oct"~total_count/(82),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="18-Dec"~total_count/(71),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="18-Dec"~total_count/(46),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="18-Nov"~total_count/(130),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="18-Nov"~total_count/(77),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="18-Oct"~total_count/(89),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="18-Oct"~total_count/(65),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="19-Dec"~total_count/(50),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="19-Dec"~total_count/(14),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="19-Nov"~total_count/(167),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="19-Nov"~total_count/(98),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="2-Dec"~total_count/(118),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="2-Dec"~total_count/(113),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="20-Dec"~total_count/(39),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="20-Dec"~total_count/(23),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="20-Nov"~total_count/(129),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="20-Nov"~total_count/(99),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="21-Nov"~total_count/(144),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="21-Nov"~total_count/(97),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="21-Oct"~total_count/(143),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="21-Oct"~total_count/(85),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="22-Nov"~total_count/(76),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="22-Nov"~total_count/(57),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="22-Oct"~total_count/(163),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="22-Oct"~total_count/(83),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="23-Oct"~total_count/(135),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="23-Oct"~total_count/(92),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="24-Oct"~total_count/(145),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="24-Oct"~total_count/(107),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="25-Nov"~total_count/(98),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="25-Nov"~total_count/(66),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="25-Oct"~total_count/(97),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="25-Oct"~total_count/(53),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="26-Nov"~total_count/(75),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="26-Nov"~total_count/(51),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="28-Oct"~total_count/(127),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="28-Oct"~total_count/(76),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="29-Oct"~total_count/(145),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="29-Oct"~total_count/(80),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="3-Dec"~total_count/(131),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="3-Dec"~total_count/(97),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="30-Oct"~total_count/(132),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="30-Oct"~total_count/(82),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="31-Oct"~total_count/(149),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="31-Oct"~total_count/(89),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="4-Dec"~total_count/(146),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="4-Dec"~total_count/(97),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="4-Nov"~total_count/(114),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="4-Nov"~total_count/(85),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="5-Dec"~total_count/(173),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="5-Dec"~total_count/(92),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="5-Nov"~total_count/(138),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="5-Nov"~total_count/(84),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="6-Dec"~total_count/(103),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="6-Dec"~total_count/(76),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="6-Nov"~total_count/(137),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="6-Nov"~total_count/(107),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="7-Nov"~total_count/(142),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="7-Nov"~total_count/(97),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="8-Nov"~total_count/(107),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="8-Nov"~total_count/(73),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="9-Dec"~total_count/(128),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="9-Dec"~total_count/(77))) %>%
  drop_na(prop_high) 
```
```{r}
daily_prop_high_fall_data <- fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(date,menu_condition,station,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop_high=case_when(item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="1-Nov"~total_count/(94),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="1-Nov"~total_count/(47),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="10-Dec"~total_count/(72),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="10-Dec"~total_count/(41),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="11-Dec"~total_count/(68),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="11-Dec"~total_count/(49),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="11-Nov"~total_count/(112),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="11-Nov"~total_count/(81),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="12-Dec"~total_count/(99),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="12-Dec"~total_count/(55),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="12-Nov"~total_count/(134),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="12-Nov"~total_count/(95),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="13-Dec"~total_count/(66),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="13-Dec"~total_count/(57),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="13-Nov"~total_count/(139),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="13-Nov"~total_count/(91),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="14-Nov"~total_count/(145),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="14-Nov"~total_count/(99),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="15-Nov"~total_count/(94),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="15-Nov"~total_count/(76),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="16-Dec"~total_count/(70),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="16-Dec"~total_count/(47),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="16-Oct"~total_count/(123),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="16-Oct"~total_count/(104),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="17-Dec"~total_count/(87),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="17-Dec"~total_count/(41),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="17-Oct"~total_count/(153),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="17-Oct"~total_count/(82),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="18-Dec"~total_count/(71),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="18-Dec"~total_count/(46),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="18-Nov"~total_count/(130),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="18-Nov"~total_count/(77),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="18-Oct"~total_count/(89),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="18-Oct"~total_count/(65),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="19-Dec"~total_count/(50),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="19-Dec"~total_count/(14),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="19-Nov"~total_count/(167),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="19-Nov"~total_count/(98),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="2-Dec"~total_count/(118),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="2-Dec"~total_count/(113),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="20-Dec"~total_count/(39),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="20-Dec"~total_count/(23),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="20-Nov"~total_count/(129),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="20-Nov"~total_count/(99),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="21-Nov"~total_count/(144),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="21-Nov"~total_count/(97),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="21-Oct"~total_count/(143),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="21-Oct"~total_count/(85),
                             item=="Grilled Hamburger"&menu_condition=="Default"&date=="22-Nov"~total_count/(76),
                             item=="Bowl Ramen Chicken"&menu_condition=="Default"&date=="22-Nov"~total_count/(57),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="22-Oct"~total_count/(163),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="22-Oct"~total_count/(83),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="23-Oct"~total_count/(135),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="23-Oct"~total_count/(92),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="24-Oct"~total_count/(145),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="24-Oct"~total_count/(107),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="25-Nov"~total_count/(98),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="25-Nov"~total_count/(66),
                             item=="Grilled Hamburger"&menu_condition=="Control"&date=="25-Oct"~total_count/(97),
                             item=="Bowl Ramen Chicken"&menu_condition=="Control"&date=="25-Oct"~total_count/(53),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="26-Nov"~total_count/(75),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="26-Nov"~total_count/(51),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="28-Oct"~total_count/(127),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="28-Oct"~total_count/(76),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="29-Oct"~total_count/(145),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="29-Oct"~total_count/(80),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="3-Dec"~total_count/(131),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="3-Dec"~total_count/(97),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="30-Oct"~total_count/(132),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="30-Oct"~total_count/(82),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="31-Oct"~total_count/(149),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="31-Oct"~total_count/(89),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="4-Dec"~total_count/(146),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="4-Dec"~total_count/(97),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="4-Nov"~total_count/(114),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="4-Nov"~total_count/(85),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="5-Dec"~total_count/(173),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="5-Dec"~total_count/(92),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="5-Nov"~total_count/(138),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="5-Nov"~total_count/(84),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="6-Dec"~total_count/(103),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="6-Dec"~total_count/(76),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="6-Nov"~total_count/(137),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="6-Nov"~total_count/(107),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="7-Nov"~total_count/(142),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="7-Nov"~total_count/(97),
                             item=="Grilled Hamburger"&menu_condition=="Carbon Label"&date=="8-Nov"~total_count/(107),
                             item=="Bowl Ramen Chicken"&menu_condition=="Carbon Label"&date=="8-Nov"~total_count/(73),
                             item=="Grilled Hamburger"&menu_condition=="Multimodal"&date=="9-Dec"~total_count/(128),
                             item=="Bowl Ramen Chicken"&menu_condition=="Multimodal"&date=="9-Dec"~total_count/(77))) %>%
  drop_na(prop_high) %>%
  mutate(date=case_when(date=="16-Oct"~"2024-10-16",
                        date=="17-Oct"~"2024-10-17",
                        date=="18-Oct"~"2024-10-18",
                        date=="21-Oct"~"2024-10-21",
                        date=="22-Oct"~"2024-10-22",
                        date=="23-Oct"~"2024-10-23",
                        date=="24-Oct"~"2024-10-24",
                        date=="25-Oct"~"2024-10-25",
                        date=="28-Oct"~"2024-10-28",
                        date=="29-Oct"~"2024-10-29",
                        date=="30-Oct"~"2024-10-30",
                        date=="31-Oct"~"2024-10-31",
                        date=="1-Nov"~"2024-11-1",
                        date=="4-Nov"~"2024-11-4",
                        date=="5-Nov"~"2024-11-5",
                        date=="6-Nov"~"2024-11-6",
                        date=="7-Nov"~"2024-11-7",
                        date=="8-Nov"~"2024-11-8",
                        date=="11-Nov"~"2024-11-11",
                        date=="12-Nov"~"2024-11-12",
                        date=="13-Nov"~"2024-11-13",
                        date=="14-Nov"~"2024-11-14",
                        date=="15-Nov"~"2024-11-15",
                        date=="18-Nov"~"2024-11-18",
                        date=="19-Nov"~"2024-11-19",
                        date=="20-Nov"~"2024-11-20",
                        date=="21-Nov"~"2024-11-21",
                        date=="22-Nov"~"2024-11-22",
                        date=="25-Nov"~"2024-11-25",
                        date=="26-Nov"~"2024-11-26",
                        date=="2-Dec"~"2024-12-2",
                        date=="3-Dec"~"2024-12-3",
                        date=="4-Dec"~"2024-12-4",
                        date=="5-Dec"~"2024-12-5",
                        date=="6-Dec"~"2024-12-6",
                        date=="9-Dec"~"2024-12-9",
                        date=="10-Dec"~"2024-12-10",
                        date=="11-Dec"~"2024-12-11",
                        date=="12-Dec"~"2024-12-12",
                        date=="13-Dec"~"2024-12-13",
                        date=="16-Dec"~"2024-12-16",
                        date=="17-Dec"~"2024-12-17",
                        date=="18-Dec"~"2024-12-18",
                        date=="19-Dec"~"2024-12-19",
                        date=="20-Dec"~"2024-12-20")) %>%
  mutate(date=as.Date(date)) 
```
```{r}
dates_vline <- as.Date(c("2024-10-28","2024-11-11","2024-11-25"))
dates_vline <- which(daily_prop_high_fall_data$date %in% dates_vline)
```

```{r}
ggplot(daily_prop_high_fall_data,aes(x=date,y=prop_high,color=station)) + 
  geom_smooth() + 
  geom_point() +
  geom_vline(xintercept=as.numeric(daily_prop_high_fall_data$date[dates_vline]),linetype=2)
```

### Proportion of medium-emitting selections???? OMG Consider fixing code for prop-low and prop-high

menu_condition level

```{r}
period_prop_middle_fall_data <- fall_data %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(menu_condition,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop=case_when(item=="Black Bean Burger"&menu_condition=="Carbon Label"~total_count/(32+159+935+74+85),
                        item=="Grilled Chicken Breast Sandwich"&menu_condition=="Carbon Label"~total_count/(32+159+935+74+85),
                        item=="Grilled Hamburger"&menu_condition=="Carbon Label"~total_count/(32+159+935+74+85),
                        item=="Seared Salmon Burger"&menu_condition=="Carbon Label"~total_count/(32+159+935+74+85),
                        item=="Trillium Grill Impossible Burger"&menu_condition=="Carbon Label"~total_count/(32+159+935+74+85),
                        item=="Black Bean Burger"&menu_condition=="Control"~total_count/(19+125+776+68+60),
                        item=="Grilled Chicken Breast Sandwich"&menu_condition=="Control"~total_count/(19+125+776+68+60),
                        item=="Grilled Hamburger"&menu_condition=="Control"~total_count/(19+125+776+68+60),
                        item=="Seared Salmon Burger"&menu_condition=="Control"~total_count/(19+125+776+68+60),
                        item=="Trillium Grill Impossible Burger"&menu_condition=="Control"~total_count/(19+125+776+68+60),
                        item=="Black Bean Burger"&menu_condition=="Default"~total_count/(33+167+904+76+90),
                        item=="Grilled Chicken Breast Sandwich"&menu_condition=="Default"~total_count/(33+167+904+76+90),
                        item=="Grilled Hamburger"&menu_condition=="Default"~total_count/(33+167+904+76+90),
                        item=="Seared Salmon Burger"&menu_condition=="Default"~total_count/(33+167+904+76+90),
                        item=="Trillium Grill Impossible Burger"&menu_condition=="Default"~total_count/(33+167+904+76+90),
                        item=="Black Bean Burger"&menu_condition=="Multimodal"~total_count/(41+165+1157+125+107),
                        item=="Grilled Chicken Breast Sandwich"&menu_condition=="Multimodal"~total_count/(41+165+1157+125+107),
                        item=="Grilled Hamburger"&menu_condition=="Multimodal"~total_count/(41+165+1157+125+107),
                        item=="Seared Salmon Burger"&menu_condition=="Multimodal"~total_count/(41+165+1157+125+107),
                        item=="Trillium Grill Impossible Burger"&menu_condition=="Multimodal"~total_count/(41+165+1157+125+107)))
period_prop_middle_fall_data
```

```{r}
period_prop_middle_fall_data %>%
  filter(item=="Grilled Chicken Breast Sandwich"|item=="Seared Salmon Burger"|item=="Trillium Grill Impossible Burger") %>%
  ggplot(aes(x=menu_condition,y=prop,fill=item)) +
  geom_col(position="dodge") +
  scale_x_discrete(limits=c("Control","Carbon Label","Default","Multimodal"))
```

```{r}
daily_prop_middle_fall_data <-fall_data %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(date,menu_condition,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop=case_when(menu_condition=="Carbon Label"&date=="1-Nov"~total_count/(94),
                        menu_condition=="Multimodal"&date=="10-Dec"~total_count/(72),
                        menu_condition=="Multimodal"&date=="11-Dec"~total_count/(68),
                        menu_condition=="Default"&date=="11-Nov"~total_count/(112),
                        menu_condition=="Multimodal"&date=="12-Dec"~total_count/(99),
                        menu_condition=="Default"&date=="12-Nov"~total_count/(134),
                        menu_condition=="Multimodal"&date=="13-Dec"~total_count/(66),
                        menu_condition=="Default"&date=="13-Nov"~total_count/(139),
                        menu_condition=="Default"&date=="14-Nov"~total_count/(145),
                        menu_condition=="Default"&date=="15-Nov"~total_count/(94),
                        menu_condition=="Multimodal"&date=="16-Dec"~total_count/(70),
                        menu_condition=="Control"&date=="16-Oct"~total_count/(123),
                        menu_condition=="Multimodal"&date=="17-Dec"~total_count/(87),
                        menu_condition=="Control"&date=="17-Oct"~total_count/(153),
                        menu_condition=="Multimodal"&date=="18-Dec"~total_count/(71),
                        menu_condition=="Default"&date=="18-Nov"~total_count/(130),
                        menu_condition=="Control"&date=="18-Oct"~total_count/(89),
                        menu_condition=="Multimodal"&date=="19-Dec"~total_count/(50),
                        menu_condition=="Default"&date=="19-Nov"~total_count/(167),
                        menu_condition=="Multimodal"&date=="2-Dec"~total_count/(118),
                        menu_condition=="Multimodal"&date=="20-Dec"~total_count/(39),
                        menu_condition=="Default"&date=="20-Nov"~total_count/(129),
                        menu_condition=="Default"&date=="21-Nov"~total_count/(144),
                        menu_condition=="Control"&date=="21-Oct"~total_count/(143),
                        menu_condition=="Default"&date=="22-Nov"~total_count/(76),
                        menu_condition=="Control"&date=="22-Oct"~total_count/(163),
                        menu_condition=="Control"&date=="23-Oct"~total_count/(135),
                        menu_condition=="Control"&date=="24-Oct"~total_count/(145),
                        menu_condition=="Multimodal"&date=="25-Nov"~total_count/(98),
                        menu_condition=="Control"&date=="25-Oct"~total_count/(97),
                        menu_condition=="Multimodal"&date=="26-Nov"~total_count/(75),
                        menu_condition=="Carbon Label"&date=="28-Oct"~total_count/(127),
                        menu_condition=="Carbon Label"&date=="29-Oct"~total_count/(145),
                        menu_condition=="Multimodal"&date=="3-Dec"~total_count/(131),
                        menu_condition=="Carbon Label"&date=="30-Oct"~total_count/(132),
                        menu_condition=="Carbon Label"&date=="31-Oct"~total_count/(149),
                        menu_condition=="Multimodal"&date=="4-Dec"~total_count/(146),
                        menu_condition=="Carbon Label"&date=="4-Nov"~total_count/(114),
                        menu_condition=="Multimodal"&date=="5-Dec"~total_count/(173),
                        menu_condition=="Carbon Label"&date=="5-Nov"~total_count/(138),
                        menu_condition=="Multimodal"&date=="6-Dec"~total_count/(103),
                        menu_condition=="Carbon Label"&date=="6-Nov"~total_count/(137),
                        menu_condition=="Carbon Label"&date=="7-Nov"~total_count/(142),
                        menu_condition=="Carbon Label"&date=="8-Nov"~total_count/(107),
                        menu_condition=="Multimodal"&date=="9-Dec"~total_count/(128))) 
```

```{r}
daily_prop_middle_fall_data <- daily_prop_middle_fall_data %>%
  filter(item=="Grilled Chicken Breast Sandwich"|item=="Seared Salmon Burger"|item=="Trillium Grill Impossible Burger") %>%
  mutate(date=case_when(date=="16-Oct"~"2024-10-16",
                        date=="17-Oct"~"2024-10-17",
                        date=="18-Oct"~"2024-10-18",
                        date=="21-Oct"~"2024-10-21",
                        date=="22-Oct"~"2024-10-22",
                        date=="23-Oct"~"2024-10-23",
                        date=="24-Oct"~"2024-10-24",
                        date=="25-Oct"~"2024-10-25",
                        date=="28-Oct"~"2024-10-28",
                        date=="29-Oct"~"2024-10-29",
                        date=="30-Oct"~"2024-10-30",
                        date=="31-Oct"~"2024-10-31",
                        date=="1-Nov"~"2024-11-1",
                        date=="4-Nov"~"2024-11-4",
                        date=="5-Nov"~"2024-11-5",
                        date=="6-Nov"~"2024-11-6",
                        date=="7-Nov"~"2024-11-7",
                        date=="8-Nov"~"2024-11-8",
                        date=="11-Nov"~"2024-11-11",
                        date=="12-Nov"~"2024-11-12",
                        date=="13-Nov"~"2024-11-13",
                        date=="14-Nov"~"2024-11-14",
                        date=="15-Nov"~"2024-11-15",
                        date=="18-Nov"~"2024-11-18",
                        date=="19-Nov"~"2024-11-19",
                        date=="20-Nov"~"2024-11-20",
                        date=="21-Nov"~"2024-11-21",
                        date=="22-Nov"~"2024-11-22",
                        date=="25-Nov"~"2024-11-25",
                        date=="26-Nov"~"2024-11-26",
                        date=="2-Dec"~"2024-12-2",
                        date=="3-Dec"~"2024-12-3",
                        date=="4-Dec"~"2024-12-4",
                        date=="5-Dec"~"2024-12-5",
                        date=="6-Dec"~"2024-12-6",
                        date=="9-Dec"~"2024-12-9",
                        date=="10-Dec"~"2024-12-10",
                        date=="11-Dec"~"2024-12-11",
                        date=="12-Dec"~"2024-12-12",
                        date=="13-Dec"~"2024-12-13",
                        date=="16-Dec"~"2024-12-16",
                        date=="17-Dec"~"2024-12-17",
                        date=="18-Dec"~"2024-12-18",
                        date=="19-Dec"~"2024-12-19",
                        date=="20-Dec"~"2024-12-20")) %>%
  mutate(date=as.Date(date)) 
```

```{r}
dates_vline <- as.Date(c("2024-10-28","2024-11-11","2024-11-25"))
dates_vline <- which(daily_prop_middle_fall_data$date %in% dates_vline)
```

```{r}
ggplot(daily_prop_middle_fall_data,aes(x=date,y=prop,color=item)) + 
  geom_smooth() + 
  geom_point() +
  geom_vline(xintercept=as.numeric(daily_prop_middle_fall_data$date[dates_vline]),linetype=2)
```

Now trying just prop of all items at grill

```{r}
daily_prop_fall_data <-fall_data %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(date,menu_condition,item) %>%
  summarise(total_count=sum(count)) %>%
  mutate(prop=case_when(menu_condition=="Carbon Label"&date=="1-Nov"~total_count/(94),
                        menu_condition=="Multimodal"&date=="10-Dec"~total_count/(72),
                        menu_condition=="Multimodal"&date=="11-Dec"~total_count/(68),
                        menu_condition=="Default"&date=="11-Nov"~total_count/(112),
                        menu_condition=="Multimodal"&date=="12-Dec"~total_count/(99),
                        menu_condition=="Default"&date=="12-Nov"~total_count/(134),
                        menu_condition=="Multimodal"&date=="13-Dec"~total_count/(66),
                        menu_condition=="Default"&date=="13-Nov"~total_count/(139),
                        menu_condition=="Default"&date=="14-Nov"~total_count/(145),
                        menu_condition=="Default"&date=="15-Nov"~total_count/(94),
                        menu_condition=="Multimodal"&date=="16-Dec"~total_count/(70),
                        menu_condition=="Control"&date=="16-Oct"~total_count/(123),
                        menu_condition=="Multimodal"&date=="17-Dec"~total_count/(87),
                        menu_condition=="Control"&date=="17-Oct"~total_count/(153),
                        menu_condition=="Multimodal"&date=="18-Dec"~total_count/(71),
                        menu_condition=="Default"&date=="18-Nov"~total_count/(130),
                        menu_condition=="Control"&date=="18-Oct"~total_count/(89),
                        menu_condition=="Multimodal"&date=="19-Dec"~total_count/(50),
                        menu_condition=="Default"&date=="19-Nov"~total_count/(167),
                        menu_condition=="Multimodal"&date=="2-Dec"~total_count/(118),
                        menu_condition=="Multimodal"&date=="20-Dec"~total_count/(39),
                        menu_condition=="Default"&date=="20-Nov"~total_count/(129),
                        menu_condition=="Default"&date=="21-Nov"~total_count/(144),
                        menu_condition=="Control"&date=="21-Oct"~total_count/(143),
                        menu_condition=="Default"&date=="22-Nov"~total_count/(76),
                        menu_condition=="Control"&date=="22-Oct"~total_count/(163),
                        menu_condition=="Control"&date=="23-Oct"~total_count/(135),
                        menu_condition=="Control"&date=="24-Oct"~total_count/(145),
                        menu_condition=="Multimodal"&date=="25-Nov"~total_count/(98),
                        menu_condition=="Control"&date=="25-Oct"~total_count/(97),
                        menu_condition=="Multimodal"&date=="26-Nov"~total_count/(75),
                        menu_condition=="Carbon Label"&date=="28-Oct"~total_count/(127),
                        menu_condition=="Carbon Label"&date=="29-Oct"~total_count/(145),
                        menu_condition=="Multimodal"&date=="3-Dec"~total_count/(131),
                        menu_condition=="Carbon Label"&date=="30-Oct"~total_count/(132),
                        menu_condition=="Carbon Label"&date=="31-Oct"~total_count/(149),
                        menu_condition=="Multimodal"&date=="4-Dec"~total_count/(146),
                        menu_condition=="Carbon Label"&date=="4-Nov"~total_count/(114),
                        menu_condition=="Multimodal"&date=="5-Dec"~total_count/(173),
                        menu_condition=="Carbon Label"&date=="5-Nov"~total_count/(138),
                        menu_condition=="Multimodal"&date=="6-Dec"~total_count/(103),
                        menu_condition=="Carbon Label"&date=="6-Nov"~total_count/(137),
                        menu_condition=="Carbon Label"&date=="7-Nov"~total_count/(142),
                        menu_condition=="Carbon Label"&date=="8-Nov"~total_count/(107),
                        menu_condition=="Multimodal"&date=="9-Dec"~total_count/(128))) %>%
  mutate(date=case_when(date=="16-Oct"~"2024-10-16",
                        date=="17-Oct"~"2024-10-17",
                        date=="18-Oct"~"2024-10-18",
                        date=="21-Oct"~"2024-10-21",
                        date=="22-Oct"~"2024-10-22",
                        date=="23-Oct"~"2024-10-23",
                        date=="24-Oct"~"2024-10-24",
                        date=="25-Oct"~"2024-10-25",
                        date=="28-Oct"~"2024-10-28",
                        date=="29-Oct"~"2024-10-29",
                        date=="30-Oct"~"2024-10-30",
                        date=="31-Oct"~"2024-10-31",
                        date=="1-Nov"~"2024-11-1",
                        date=="4-Nov"~"2024-11-4",
                        date=="5-Nov"~"2024-11-5",
                        date=="6-Nov"~"2024-11-6",
                        date=="7-Nov"~"2024-11-7",
                        date=="8-Nov"~"2024-11-8",
                        date=="11-Nov"~"2024-11-11",
                        date=="12-Nov"~"2024-11-12",
                        date=="13-Nov"~"2024-11-13",
                        date=="14-Nov"~"2024-11-14",
                        date=="15-Nov"~"2024-11-15",
                        date=="18-Nov"~"2024-11-18",
                        date=="19-Nov"~"2024-11-19",
                        date=="20-Nov"~"2024-11-20",
                        date=="21-Nov"~"2024-11-21",
                        date=="22-Nov"~"2024-11-22",
                        date=="25-Nov"~"2024-11-25",
                        date=="26-Nov"~"2024-11-26",
                        date=="2-Dec"~"2024-12-2",
                        date=="3-Dec"~"2024-12-3",
                        date=="4-Dec"~"2024-12-4",
                        date=="5-Dec"~"2024-12-5",
                        date=="6-Dec"~"2024-12-6",
                        date=="9-Dec"~"2024-12-9",
                        date=="10-Dec"~"2024-12-10",
                        date=="11-Dec"~"2024-12-11",
                        date=="12-Dec"~"2024-12-12",
                        date=="13-Dec"~"2024-12-13",
                        date=="16-Dec"~"2024-12-16",
                        date=="17-Dec"~"2024-12-17",
                        date=="18-Dec"~"2024-12-18",
                        date=="19-Dec"~"2024-12-19",
                        date=="20-Dec"~"2024-12-20")) %>%
  mutate(date=as.Date(date)) 
```

```{r}
dates_vline <- as.Date(c("2024-10-28","2024-11-11","2024-11-25"))
dates_vline <- which(daily_prop_fall_data$date %in% dates_vline)
```

```{r}
ggplot(daily_prop_fall_data,aes(x=date,y=prop,color=item)) + 
  geom_smooth() + 
  geom_point() +
  geom_vline(xintercept=as.numeric(daily_prop_fall_data$date[dates_vline]),linetype=2)
```

### Mean carbon costs 

```{r}
fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(menu_condition,station) %>%
  summarise(tot_carbon_cost=sum(corr_carbon_cost),tot_water_cost=sum(corr_water_cost),tot_dollar_cost=sum(corr_dollar_cost),tot_sales=sum(count)) %>%
  mutate(mean_carbon_cost=tot_carbon_cost/tot_sales) %>%
  mutate(mean_water_cost=tot_water_cost/tot_sales) %>%
  mutate(mean_spend=tot_dollar_cost/tot_sales) %>%
  ggplot(aes(x=menu_condition,y=mean_carbon_cost,fill=station)) + 
  geom_col(position="dodge") + 
  scale_x_discrete(limits=c("Control","Carbon Label","Default","Multimodal"))
```

```{r}
mean_per_day_carbon_cost_fall_data <- fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(date,menu_condition,station) %>%
  summarise(total_carbon_cost=sum(corr_carbon_cost),total_sales=sum(count)) %>%
  mutate(mean_carbon_cost=total_carbon_cost/total_sales) %>%
  mutate(date=case_when(date=="16-Oct"~"2024-10-16",
                        date=="17-Oct"~"2024-10-17",
                        date=="18-Oct"~"2024-10-18",
                        date=="21-Oct"~"2024-10-21",
                        date=="22-Oct"~"2024-10-22",
                        date=="23-Oct"~"2024-10-23",
                        date=="24-Oct"~"2024-10-24",
                        date=="25-Oct"~"2024-10-25",
                        date=="28-Oct"~"2024-10-28",
                        date=="29-Oct"~"2024-10-29",
                        date=="30-Oct"~"2024-10-30",
                        date=="31-Oct"~"2024-10-31",
                        date=="1-Nov"~"2024-11-1",
                        date=="4-Nov"~"2024-11-4",
                        date=="5-Nov"~"2024-11-5",
                        date=="6-Nov"~"2024-11-6",
                        date=="7-Nov"~"2024-11-7",
                        date=="8-Nov"~"2024-11-8",
                        date=="11-Nov"~"2024-11-11",
                        date=="12-Nov"~"2024-11-12",
                        date=="13-Nov"~"2024-11-13",
                        date=="14-Nov"~"2024-11-14",
                        date=="15-Nov"~"2024-11-15",
                        date=="18-Nov"~"2024-11-18",
                        date=="19-Nov"~"2024-11-19",
                        date=="20-Nov"~"2024-11-20",
                        date=="21-Nov"~"2024-11-21",
                        date=="22-Nov"~"2024-11-22",
                        date=="25-Nov"~"2024-11-25",
                        date=="26-Nov"~"2024-11-26",
                        date=="2-Dec"~"2024-12-2",
                        date=="3-Dec"~"2024-12-3",
                        date=="4-Dec"~"2024-12-4",
                        date=="5-Dec"~"2024-12-5",
                        date=="6-Dec"~"2024-12-6",
                        date=="9-Dec"~"2024-12-9",
                        date=="10-Dec"~"2024-12-10",
                        date=="11-Dec"~"2024-12-11",
                        date=="12-Dec"~"2024-12-12",
                        date=="13-Dec"~"2024-12-13",
                        date=="16-Dec"~"2024-12-16",
                        date=="17-Dec"~"2024-12-17",
                        date=="18-Dec"~"2024-12-18",
                        date=="19-Dec"~"2024-12-19",
                        date=="20-Dec"~"2024-12-20")) %>%
  mutate(date=as.Date(date)) 
```

```{r}
dates_vline <- as.Date(c("2024-10-28","2024-11-11","2024-11-25"))
dates_vline <- which(mean_per_day_carbon_cost_fall_data$date %in% dates_vline)
```

```{r}
ggplot(mean_per_day_carbon_cost_fall_data,aes(x=date,y=mean_carbon_cost,color=station)) + 
  geom_smooth() + 
  geom_point() +
  geom_vline(xintercept=as.numeric(mean_per_day_carbon_cost_fall_data$date[dates_vline]),linetype=2)
```

### Mean spend

```{r}
fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(menu_condition,station) %>%
  summarise(tot_carbon_cost=sum(corr_carbon_cost),tot_water_cost=sum(corr_water_cost),tot_dollar_cost=sum(corr_dollar_cost),tot_sales=sum(count)) %>%
  mutate(mean_carbon_cost=tot_carbon_cost/tot_sales) %>%
  mutate(mean_water_cost=tot_water_cost/tot_sales) %>%
  mutate(mean_spend=tot_dollar_cost/tot_sales) %>%
  ggplot(aes(x=menu_condition,y=mean_spend,fill=station)) + 
  geom_col(position="dodge") + 
  scale_x_discrete(limits=c("Control","Carbon Label","Default","Multimodal","Multimodal (Extra)"))
```

```{r}
mean_daily_spend_fall_data <- fall_data %>%
  filter(station_type=="Treatment") %>%
  filter(item_cat=="Main") %>%
  group_by(date,menu_condition,station) %>%
  summarise(total_spend=sum(corr_dollar_cost),total_sales=sum(count)) %>%
  mutate(mean_spend=total_spend/total_sales) %>%
  mutate(date=case_when(date=="16-Oct"~"2024-10-16",
                        date=="17-Oct"~"2024-10-17",
                        date=="18-Oct"~"2024-10-18",
                        date=="21-Oct"~"2024-10-21",
                        date=="22-Oct"~"2024-10-22",
                        date=="23-Oct"~"2024-10-23",
                        date=="24-Oct"~"2024-10-24",
                        date=="25-Oct"~"2024-10-25",
                        date=="28-Oct"~"2024-10-28",
                        date=="29-Oct"~"2024-10-29",
                        date=="30-Oct"~"2024-10-30",
                        date=="31-Oct"~"2024-10-31",
                        date=="1-Nov"~"2024-11-1",
                        date=="4-Nov"~"2024-11-4",
                        date=="5-Nov"~"2024-11-5",
                        date=="6-Nov"~"2024-11-6",
                        date=="7-Nov"~"2024-11-7",
                        date=="8-Nov"~"2024-11-8",
                        date=="11-Nov"~"2024-11-11",
                        date=="12-Nov"~"2024-11-12",
                        date=="13-Nov"~"2024-11-13",
                        date=="14-Nov"~"2024-11-14",
                        date=="15-Nov"~"2024-11-15",
                        date=="18-Nov"~"2024-11-18",
                        date=="19-Nov"~"2024-11-19",
                        date=="20-Nov"~"2024-11-20",
                        date=="21-Nov"~"2024-11-21",
                        date=="22-Nov"~"2024-11-22",
                        date=="25-Nov"~"2024-11-25",
                        date=="26-Nov"~"2024-11-26",
                        date=="2-Dec"~"2024-12-2",
                        date=="3-Dec"~"2024-12-3",
                        date=="4-Dec"~"2024-12-4",
                        date=="5-Dec"~"2024-12-5",
                        date=="6-Dec"~"2024-12-6",
                        date=="9-Dec"~"2024-12-9",
                        date=="10-Dec"~"2024-12-10",
                        date=="11-Dec"~"2024-12-11",
                        date=="12-Dec"~"2024-12-12",
                        date=="13-Dec"~"2024-12-13",
                        date=="16-Dec"~"2024-12-16",
                        date=="17-Dec"~"2024-12-17",
                        date=="18-Dec"~"2024-12-18",
                        date=="19-Dec"~"2024-12-19",
                        date=="20-Dec"~"2024-12-20")) %>%
  mutate(date=as.Date(date)) 
```

```{r}
dates_vline <- as.Date(c("2024-10-28","2024-11-11","2024-11-25"))
dates_vline <- which(mean_daily_spend_fall_data$date %in% dates_vline)
```

```{r}
ggplot(mean_daily_spend_fall_data,aes(x=date,y=mean_spend,color=station)) + 
  geom_smooth() + 
  geom_point() +
  geom_vline(xintercept=as.numeric(mean_daily_spend_fall_data$date[dates_vline]),linetype=2)
```







We'll need to do checks to see whether there are differences in the purchase of different item categories across menu conditions, whether there are differences in the sales total across menu conditions, differences in the number of observation days across menu conditions, differences in the daily sales average across menu conditions 

Spillover within meal period and between meal period 

also look at diminishing effects over time by looking at outcomes at day level, not just by period 











need to figure out modifications sales between periods because that changes the denominator

```{r}
fall_data %>%
  filter(station=="Grill") %>%
  group_by(menu_condition,item_cat) %>%
  summarise(sum(count)) 
```


### Between-Condition Observational Differences

We'll first evaluate the differences in the number of observation days and sales counts across study periods.  

* Differences in the number of observation days across menu conditions:

menu_condition

```{r}
fall_data %>%
  group_by(menu_condition,date) %>%
  summarise(count=n()) %>%
  mutate(day_count=1) %>%
  summarise(observation_days=sum(day_count))
```

* Differences in global sales volume across menu conditions: 

```{r}
fall_data %>%
  group_by(menu_condition,date) %>%
  summarise(count=n()) %>%
  group_by(menu_condition) %>%
  summarise(sales_count=sum(count))
```


* Daily Sales volume 



### Grill - Mains - Prop

```{r}
fall_data %>%
  filter(menu_condition=="Control") %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(19+125+776+68+60)) %>%
  mutate(condition="Control")
```

```{r}
fall_data %>%
  filter(menu_condition=="Carbon Label") %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(32+159+935+74+85)) %>%
  mutate(condition="Carbon Label")
```

```{r}
fall_data %>%
  filter(menu_condition=="Default") %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(33+167+904+76+90)) %>%
  mutate(condition="Default")
```

```{r}
fall_data %>%
  filter(menu_condition=="Multimodal") %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(27+84+624+59+50)) %>%
  mutate(condition="Multimodal")
```

```{r}
fall_data %>%
  filter(menu_condition=="Multimodal (Extra)") %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(14+81+533+66+57)) %>%
  mutate(condition="Multimodal (Extra)")
```

```{r}
fall_data %>%
  filter(menu_condition=="Multimodal (Extra)"| menu_condition=="Multimodal") %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(41+165+1157+125+107)) %>%
  mutate(condition="Multimodal (Full)")
```

### Ramen - Mains - Prop

```{r}
fall_data %>%
  filter(menu_condition=="Control") %>%
  filter(station=="Ramen") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(563+108)) %>%
  mutate(condition="Control")
```

```{r}
fall_data %>%
  filter(menu_condition=="Carbon Label") %>%
  filter(station=="Ramen") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(685+135)) %>%
  mutate(condition="Carbon Label")
```

```{r}
fall_data %>%
  filter(menu_condition=="Default") %>%
  filter(station=="Ramen") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(698+172)) %>%
  mutate(condition="Default")
```

```{r}
fall_data %>%
  filter(menu_condition=="Multimodal") %>%
  filter(station=="Ramen") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(483+109)) %>%
  mutate(condition="Multimodal")
```

```{r}
fall_data %>%
  filter(menu_condition=="Multimodal (Extra)") %>%
  filter(station=="Ramen") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(377+73)) %>%
  mutate(condition="Multimodal (Extra)")
```

```{r}
fall_data %>%
  filter(menu_condition=="Multimodal (Extra)" | menu_condition=="Multimodal") %>%
  filter(station=="Ramen") %>%
  filter(item_cat=="Main") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) %>%
  mutate(prop=item_count/(860+182)) %>%
  mutate(condition="Multimodal (Full)")
```

### Grill - Mains and Modifications - Prop


```{r}
fall_data %>%
  filter(menu_condition=="Control") %>%
  filter(station=="Grill") %>%
  filter(item_cat=="Main" | item_cat=="Modification") %>%
  group_by(item) %>%
  summarise(item_count=sum(count)) 
```















CONSIDER distance between highest-carbon offering and next-lowest offering between stations
Price relativity 
Number of veg options
 










differnce in carbon estiamte for highest and lowest 
number of options to choose between

Sides and modifications not factored in currently 

also measure spillover across other stations during same meal interval

measure spillover across other meal interval


### Foot Traffic

```{r}
foot_traffic_data %>%
  select(date,time,count,menu_condition) %>%
  distinct(time)
```

```{r}
foot_traffic_data %>%
  select(date,time,count,menu_condition) %>%
  group_by(menu_condition,time) %>%
  summarise(transaction_volume=mean(count)) 
head(5)
```


```{r}
foot_traffic_data %>%
  select(date,time,count,menu_condition) %>%
  group_by(menu_condition,time) %>%
  summarise(transaction_volume=mean(count)) %>%
  ggplot(aes(x=time,y=transaction_volume,fill=menu_condition)) + 
  geom_col(position="dodge") +
  scale_x_discrete(limits=c("6:15 AM","6:30 AM","6:45 AM","7:00 AM","7:15 AM","7:30 AM","7:45 AM","8:00 AM","8:15 AM","8:30 AM","8:45 AM","9:00 AM","9:15 AM","9:30 AM","9:45 AM","10:00 AM","10:15 AM","10:30 AM","10:45 AM","11:00 AM","11:15 AM","11:30 AM","11:45 AM","12:00 PM","12:15 PM","12:30 PM","12:45 PM","1:00 PM","1:15 PM","1:30 PM","1:45 PM","2:00 PM","2:15 PM","2:30 PM","2:45 PM","3:00 PM","3:15 PM","3:30 PM","3:45 PM","4:00 PM"))
```

```{r}

```

sales_data %>%
  mutate(item_cat=case_when(item=="Quesadilla Deluxe Trillium"~"Main",
                           item=="Grilled Hamburger"~"Main",
                           item=="Fried Chicken Tenders"~"Main",
                           item=="Burrito Una Mano Trillium BYO"~"Main",
                           item=="French Fries"~"Side",
                           item=="Quesadilla Cheese"~"Ma
